Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-29 xrb2/paper.tex
reaction pathways -> burning tracjectories

The mean molecular weight $\bar{A}$ within each of our simulations seems to grow along defined tracks confined to certain temperatures $T$, as shown in the Figure \ref{fig:abar} phase plots. We believe that the tracks in the plot correspond to reaction pathways in the reaction network. Comparing Figure \ref{fig:abar} to \citet{flame_wave1}, these tracks are much more neat and clearly defined. The ``messiness" of the tracks may be dependent on how mixed the flame interior is. Since these new simulations are un-boosted, they may be inherently less mixed than those in \citet{flame_wave1}. {\tt F1000} aligns with this interpretation: its $\bar{A}$ tracks are somewhat disrupted compared to the slower rotation runs, possibly due to the more vigorous mixing of the vortex at the flame front. Comparing the different runs, we also see that as the rotation rate increases, so does the peak temperature. This makes sense if higher rotation leads to a more concentrated, intense vortex near the flame front. It also agrees with our earlier interpretation of the enhanced burning seen in Figure \ref{fig:time_series_1000} for {\tt F1000}.

@@

Figure~\ref{fig:compare_500Hz_abar} shows $\bar{A}$ for three $500~\mathrm{Hz}$ simulations with different initial temperature structures ($T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$) at $t = 70~\mathrm{ms}$. We do not plot $\tt{F500\_4E8}$ here because it fails to form a clear burning front. $\tt{F500\_3E8}$ (Figure~\ref{fig:compare_500Hz_abar}, bottom panel) --- the hottest run to form a clear burning front --- has a faster propagating flame (this will be discussed further in Section \ref{ssec:temp_prop}). It also reaches slightly higher $\bar{A}$ values than the two cooler runs. The Figure~\ref{fig:abar_hot} $\bar{A}$-$T$ phase plots of $\tt{F500}$ (left) and $\tt{F500\_3E8}$ (middle) also reflect these $\bar{A}$ features, with $\tt{F500\_3E8}$ reaching slightly higher $\bar{A}$ values. $\tt{F500\_3E8}$ also reaches higher $\enucdot$ values at the low end of the temperature range ($< 0.5 \times 10^9~\mathrm{K}$). There appear to be more causally connected regions across a range of $\bar{A}$ at low temperatures for $\tt{F500\_3E8}$ than for $\tt{F500}$, suggesting that the higher $\enucdot$ for $\tt{F500\_3E8}$ generates burning in certain reaction pathways that are not present in the cooler $\tt{F500}$ run. Note that, although $\tt{F500\_3E8}$ is the hottest run with a modified initial temperature configuration to form a distinct flame front, the highest rotation $\tt{F1000}$ flame actually reaches higher temperatures (see Figure~\ref{fig:maxima}, left panel) as well as higher $\bar{A}$ (see Figure~\ref{fig:time_series_1000}).

@@

 Though $\tt{F500\_4E8}$ does not form a distinct burning front, it does achieve greatly enhanced burning, as shown in the Figure~\ref{fig:abar_hot} $\bar{A}$-$T$ phase plot (right panel). Not only is $\tt{F500\_4E8}$ significantly hotter overall compared to all other runs, but there is a large causally connected region across a wide range of $\bar{A}$. This indicates that the hotter temperature has facilitated significant burning in reaction pathways that were not favored at the lower temperatures. The reaction pathways are also very disrupted for $\tt{F500\_4E8}$ compared to the cooler runs, suggesting that the hotter temperature leads to more vigorous mixing. Indeed, this appears to be the case looking at Figure~\ref{fig:4e8_stacked_abar} and the right panel of Figure~\ref{fig:uv_hot} (discussed further in section~\ref{ssec:temp_prop}). The disrupted reaction pathways resemble those found in Figure \ref{fig:abar} for the highest rotation $\tt{F1000}$ run, though they are even more dramatically disrupted for $\tt{F500\_4E8}$. $\tt{F500\_4E8}$ is also noticeably hotter than $\tt{F1000}$, even though it is run for significantly less time ($t = 40~\mathrm{ms}$ vs $t = 100~\mathrm{ms}$). Although the $\tt{F500\_4E8}$ run is clearly a special case in that it develops steady burning across the domain rather than a propagating flame, enhanced burning in this hottest run aligns with results from the other simulations with differing initial temperature structures. As $T_{\mathrm{star}}$ is increased, the overall behavior and propagation of the flame is significantly altered, implying that burning is very temperature-sensitive. We explore flame propagation further in Section~\ref{ssec:temp_prop}.

>>>>

The mean molecular weight $\bar{A}$ within each of our simulations seems to grow along defined tracks confined to certain temperatures $T$, as shown in the Figure \ref{fig:abar} phase plots. We believe that the tracks in the plot correspond to burning trajectories in the reaction network. Comparing Figure \ref{fig:abar} to \citet{flame_wave1}, these tracks are much more neat and clearly defined. The ``messiness" of the tracks may be dependent on how mixed the flame interior is. Since these new simulations are un-boosted, they may be inherently less mixed than those in \citet{flame_wave1}. {\tt F1000} aligns with this interpretation: its $\bar{A}$ tracks are somewhat disrupted compared to the slower rotation runs, possibly due to the more vigorous mixing of the vortex at the flame front. Comparing the different runs, we also see that as the rotation rate increases, so does the peak temperature. This makes sense if higher rotation leads to a more concentrated, intense vortex near the flame front. It also agrees with our earlier interpretation of the enhanced burning seen in Figure \ref{fig:time_series_1000} for {\tt F1000}.

@@

Figure~\ref{fig:compare_500Hz_abar} shows $\bar{A}$ for three $500~\mathrm{Hz}$ simulations with different initial temperature structures ($T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$) at $t = 70~\mathrm{ms}$. We do not plot $\tt{F500\_4E8}$ here because it fails to form a clear burning front. $\tt{F500\_3E8}$ (Figure~\ref{fig:compare_500Hz_abar}, bottom panel) --- the hottest run to form a clear burning front --- has a faster propagating flame (this will be discussed further in Section \ref{ssec:temp_prop}). It also reaches slightly higher $\bar{A}$ values than the two cooler runs. The Figure~\ref{fig:abar_hot} $\bar{A}$-$T$ phase plots of $\tt{F500}$ (left) and $\tt{F500\_3E8}$ (middle) also reflect these $\bar{A}$ features, with $\tt{F500\_3E8}$ reaching slightly higher $\bar{A}$ values. $\tt{F500\_3E8}$ also reaches higher $\enucdot$ values at the low end of the temperature range ($< 0.5 \times 10^9~\mathrm{K}$). There appear to be more causally connected regions across a range of $\bar{A}$ at low temperatures for $\tt{F500\_3E8}$ than for $\tt{F500}$, suggesting that the higher $\enucdot$ for $\tt{F500\_3E8}$ generates burning in certain burning trajectories that are not present in the cooler $\tt{F500}$ run. Note that, although $\tt{F500\_3E8}$ is the hottest run with a modified initial temperature configuration to form a distinct flame front, the highest rotation $\tt{F1000}$ flame actually reaches higher temperatures (see Figure~\ref{fig:maxima}, left panel) as well as higher $\bar{A}$ (see Figure~\ref{fig:time_series_1000}).

@@

 Though $\tt{F500\_4E8}$ does not form a distinct burning front, it does achieve greatly enhanced burning, as shown in the Figure~\ref{fig:abar_hot} $\bar{A}$-$T$ phase plot (right panel). Not only is $\tt{F500\_4E8}$ significantly hotter overall compared to all other runs, but there is a large causally connected region across a wide range of $\bar{A}$. This indicates that the hotter temperature has facilitated significant burning in burning trajectories that were not favored at the lower temperatures. The burning trajectories are also very disrupted for $\tt{F500\_4E8}$ compared to the cooler runs, suggesting that the hotter temperature leads to more vigorous mixing. Indeed, this appears to be the case looking at Figure~\ref{fig:4e8_stacked_abar} and the right panel of Figure~\ref{fig:uv_hot} (discussed further in section~\ref{ssec:temp_prop}). The disrupted burning trajectories resemble those found in Figure \ref{fig:abar} for the highest rotation $\tt{F1000}$ run, though they are even more dramatically disrupted for $\tt{F500\_4E8}$. $\tt{F500\_4E8}$ is also noticeably hotter than $\tt{F1000}$, even though it is run for significantly less time ($t = 40~\mathrm{ms}$ vs $t = 100~\mathrm{ms}$). Although the $\tt{F500\_4E8}$ run is clearly a special case in that it develops steady burning across the domain rather than a propagating flame, enhanced burning in this hottest run aligns with results from the other simulations with differing initial temperature structures. As $T_{\mathrm{star}}$ is increased, the overall behavior and propagation of the flame is significantly altered, implying that burning is very temperature-sensitive. We explore flame propagation further in Section~\ref{ssec:temp_prop}.
